Titeln på avhandlingens språk

### 2022-11-05 intro.tex
tweaking intro

In this paper, we introduce the first, to our knowledge, data-driven model for human timings in \ac{WCA} applications.
Using the data collected for \textcite{olguinmunoz:impact2021} as a base, we build a stochastic model which takes as input past measurements of system responsiveness and produces realistic step execution times.
Furthermore, we introduce a novel way to generate dynamic traces of frames for \ac{WCA} applications which can be combined with the timing model for a full end-to-end emulation of a human.

Our contributions build on previous work on the characterization of human perception of delay in \ac{WCA} systems.
We expand upon the findings of \textcite{Ha2014towards,Chen2017Empirical}, who identified the need and opportunities for edge offloading of \ac{WCA} and characterized latency bounds in these systems.
Furthermore, we directly build upon and expand on our previous work on the modeling of human behavior and characterization of human timings in \ac{WCA}
In \textcite{olguin2018scaling,olguin2019edgedroid} we introduced a coarse approximation to human behavior modeling in \ac{WCA} we called \emph{EdgeDroid}.
We used a trace-driven approach, where a pre-recorded and pre-processed ``ideal'' trace of steps for a specific \ac{WCA} step-based task is replayed to a Gabriel~\cite{Chen2018application} backend.
In order to adapt to potential mismatches between system responsiveness at trace-capture time and trace-replay time, we used a simple \ac{FSM} to adapt the trace at the latter by replaying or skipping certain segments.
In \textcite{olguinmunoz:impact2021} we studied the effects of reduced system responsiveness on human behavior in \ac{WCA} applications through human-subject studies.
We found that humans generally pace themselves according to the perceived system responsiveness.
When interacting with a highly responsive system, humans tended to speed up with each step; conversely, humans tended to slow down in highly unresponsive states.

We name the new model presented in this paper \emph{\edgedroid}; a direct, more realistic evolution of our initial EdgeDroid approach.
\todo[inline]{What is our goal with this?}

>>>>

\medskip

With that context, we can express the contributions of this paper as follows:
\begin{enumerate}
    \item\label{item:contrib:model} We introduce the first, to our knowledge, data-driven model for human timings in \ac{WCA} applications.
    Using the data collected for \textcite{olguinmunoz:impact2021} as a base, we build a stochastic model which takes as input past measurements of system responsiveness and produces realistic step execution times.
    \item\label{item:contrib:frames} We introduce a novel way to generate dynamic traces of frames for \ac{WCA} applications which can be combined with the timing model for a full end-to-end emulation of a human.
    \item Finally, using \cref{item:contrib:model,item:contrib:frames}, we explore the potential for optimization in these systems, and propose a novel strategy for the optimum sampling of \ac{WCA} applications with respect to the number of video frames captured per step.
\end{enumerate}

Our contributions build on previous work on the characterization of human perception of delay in \ac{WCA} systems.
We expand upon the findings of \textcite{Ha2014towards,Chen2017Empirical}, who identified the need and opportunities for edge offloading of \ac{WCA} and characterized latency bounds in these systems.

Furthermore, we directly build upon and expand on our previous work on the modeling of human behavior and characterization of human timings in \ac{WCA}, as well as on optimum sampling of edge-bound interactive systems.
In \textcite{olguin2018scaling,olguin2019edgedroid} we introduced a coarse approximation to human behavior modeling in \ac{WCA} we called \emph{EdgeDroid}.
We used a trace-driven approach, where a pre-recorded and pre-processed ``ideal'' trace of steps for a specific \ac{WCA} step-based task is replayed to a Gabriel~\cite{Chen2018application} backend.
In order to adapt to potential mismatches between system responsiveness at trace-capture time and trace-replay time, we used a simple \ac{FSM} to adapt the trace at the latter by replaying or skipping certain segments.
In \textcite{olguinmunoz:impact2021} we studied the effects of reduced system responsiveness on human behavior in \ac{WCA} applications through human-subject studies.
We found that humans generally pace themselves according to the perceived system responsiveness.
When interacting with a highly responsive system, humans tended to speed up with each step; conversely, humans tended to slow down in highly unresponsive states.
We name the new model presented in this paper \emph{\edgedroid}; a direct, more realistic evolution of our initial EdgeDroid approach.
Finally, in \textcite{ICCperiodic1,TMCperiodic} we find the optimum periodic sampling interval which minimizes the energy tracking human progress of a specific subtask in \ac{WCA}.
This is further extended into an aperiodic strategy in \textcite{secAperiodic}.
